Adaptive Preregistration for Modelling

### 2024-01-24 preregistration_modelling.qmd

::: callout-note
## Preregistration Item

*During this process, observed data, or data and patterns that guided model design and calibration is compared to model output in order to identify if and where there are any systematic differences.*

>>>>

*During this process, observed data, or data and patterns that guided model design and calibration, are compared to model output in order to identify if and where there are any systematic differences.*
